Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-07-21 doc/PRF2022/PRF_main.tex
yny July20 10

\section{Results}
\label{sec:results}
In this section, we subject the Janus particle structures to various background
flows.  The purpose of this study is to understand how self-assembled particles
respond to external fluid forcing.  We can then compare the results to guage
the effective properties of materials comprised of Janus particles as a function
of their amphiphilic properties.  
%%%
%%%
\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure4.pdf}
  \end{center}
  \caption{
    \label{fig:Ves_shear}
The figure shows a single vesicle in a shear flow. Panels (a)-(c) are snapshots for $\dot \gamma = \{0.05, 0.0655, 0.075\}$ at $t=0.16\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a).
The streamlines are plotted in the background.
Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
     }
\end{figure}

\subsection{Bilayer configurations (bc(i)) in a linear shear flow}
To begin, we place the bilayer structure (with bc(i)) from the inset of Figure~\ref{fig:relax}(b)
in a linear shear flow
\begin{equation}
\uu_\infty(\xx) = \dot\gamma \text{ ns }^{-1} ({\bf e}_y\cdot\xx){\bf e}_x,
\end{equation}
%
where $\dot\gamma$ is the dimensionless shear rate and ${\bf e}_x$ and ${\bf e}_y$
are horizontal and vertical unit vectors, respectively.  
The initial bilayer structure consists of a small self-enclosing bilayer (vesicle) and several pieces of bilayers.
Figure~\ref{fig:BC1_shear}(a)--(c)
shows snapshots of the bilayer when $\dot\gamma= 0.05,0.075,0.01$
at $t = 0.5$ $\upmu$s.
The dynamics of the bilayer can be found in the supplementary movies, which show that the initial pieces of bilayers merge and form a worm-like shape
under a linear shear flow.
At a low shear rate, the bilayer constantly goes through rotation and extensional deformation with the whole bilayer intact (figure~\ref{fig:BC1_shear}(a)).
As the shear rate increases to a moderate value (figure~\ref{fig:BC1_shear}(b)), the bilayer is observed to shed a small piece of bilayer, similar to the asymmetric breakup of a viscous drop \cite{}.
In figure~\ref{fig:BC1_shear}(c) the high shear rate gives rise to two nearly equal bilayers, similar to the symmetric drop breakup under a linear shear flow \cite{}.
%
\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure5.pdf}    
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC1_TG} Multiple component bilayers in a Taylor-Green when $V_0 = \{0.1, 0.15, 0.2\}$ at $t=0.2\ \mu$s. The pre-relaxed initial configuration is shown in inset of panel (a). 
 The streamlines are plotted in the background. 
Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
  }
\end{figure}

In terms of deformations, 
the free energies 
are relatively constant (Figure~\ref{fig:BC1_shear}(d)),
with the overall changes in the range of a few kT/nm.  
Note that the free energy $F$ in figure~\ref{fig:BC1_shear}(d) has the unit of force because our system is two dimensional.

An interesting feature of the simulations is that the order parameter $\tilde S_2$ in (Figure~\ref{fig:BC1_shear}(e))
is on average increasing.  In the initial configuration,
the structure has three or four components.  
%
Under the shear flow, the shedding and merging of bilayers
result in an overall decrease in distinct bilayer structures.  
This suggests that
the shear flow changes the energy landscape to move the local equilibrium obtained from a random initial condition
to an alternate local equilibrium with greater orientational order.

\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure6.pdf}        
  \end{center}
\caption{\label{fig:ves_TG} Single vesicle in a TG flow. Panels (a)-(c) are snapshots for $V_0=\{0.1, 0.15, 0.2\}$ at $t=0.6\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a). The streamlines are plotted in the background.
Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
}
\end{figure}
%
Finally, the strain parameter diverges in the large shear flow rate cases (Figure~\ref{fig:BC1_shear}(f))
because the components eventually completely separate and move away from one another
under the shear flow.

In \citet{Fu2022_JFM} the hydrodynamics of a JP vesicle under a linear shear flow is studied. 
Focusing on drawing analogies to hydrodynamics of a vesicle in continuum modeling (such as tank-treading, bilayer slip and permeability),
our previous studies also show the existence of a critical shear rate above which the JP vesicle ruptures. 
Based on the these early results, we conduct numerical simulations with $\dot\gamma=0.05, 0.066, 0.075$.
At these shear rates, the vesicle undergoes the familiar hydrodynamics (such as elongation along the extensional axis and tank-treading motion),
as shown in Figure~\ref{fig:Ves_shear} (a)--(c).
%
Here we illustrate how the three measures of structural deformation 
correlate to the dynamics of a JP vesicle.
We reinitialized the case (i) configuration with particles arranged in the pattern of a single, circular vesicle.
This shape is also a local equilibrium, with somewhat less energy than the disordered state c.f.,
Figure~\ref{fig:BC1_shear}(d) and Figure~\ref{fig:Ves_shear} (d).

Unlike the dynamics of bilayers in figure~\ref{fig:BC1_shear}, 
the energies of the JP vesicle in figure~\ref{fig:Ves_shear}(d) show jumps from the baseline value $30$ kT/nm to 32 kT/nm
signaling the rupture of the vesicle into multiple components
(Figure \ref{fig:Ves_shear}(d), long and short dashed curves).
After this initial break, the energies are more or less constant.

For the lowest shear rate case, the vesicle has nearly constant orientational order $\tilde S_2 = 1$
(Figure \ref{fig:Ves_shear}(e), solid curve).
Following rupture ($\dot\gamma= 0.066$ and $\dot \gamma= 0.075$),
there is greater variation in the order parameter $\tilde{S}_2$
with a baseline value around $0.7$
(Figure \ref{fig:Ves_shear}(e), dashed curves).
The oscillations occur due to the orbit of the two bilayer components,
and $\tilde{S}_2$ increases to about $0.9$ when the components slide past one another and are nearly parallel.

Like with multiple component bilayer case, positional order diverges when the components of the ruptured
vesicle separate and drift off in opposite directions (Figure \ref{fig:Ves_shear}(f), dashed curves).

%%%%%%%
\subsection{Bilayer and vesicle configurations in a Taylor-Green flow}
Next, we subject the bilayer/vesicles configurations to a 
Taylor-Green (TG) background flow
\begin{equation}
\label{eq:tg_flow}
\uu_\infty(\xx) = V_0\; \frac{\text{nm}}{\text{ns}}\;
\left(
-\cos\left(\frac{{\bf e}_x\cdot\xx}{\lambda}\right)
 \sin\left(\frac{{\bf e}_y\cdot\xx}{\lambda}\right)
         {\bf e}_x
         +\sin\left(\frac{{\bf e}_x\cdot\xx}{\lambda}\right)
         \cos\left(\frac{{\bf e}_y\cdot\xx}{\lambda}\right)
             {\bf e}_y\right).
\end{equation}
The TG flow is a confining flow consisting of a checkboard pattern
of cells with alternating circulation.  We control the flow by the
the dimensionless flow strength $V_0$ and with the cell size $\lambda = l$ nm.
The default parameter $l=2$ is used through this work.
%

>>>>

\section{Results}
\label{sec:results}
In this section, we subject the Janus particle structures to various background
flows.  The purpose of this study is to understand how self-assembled particles
respond to external fluid forcing.  We can then compare the results to guage
the effective properties of materials comprised of Janus particles as a function
of their amphiphilic properties.  
%%%

\subsection{Bilayer configurations (bc(i)) in a linear shear flow}
To begin, we place the bilayer structure (with bc(i)) from the inset of Figure~\ref{fig:relax}(b)
in a linear shear flow
\begin{equation}
\uu_\infty(\xx) = \dot\gamma \text{ ns }^{-1} ({\bf e}_y\cdot\xx){\bf e}_x,
\end{equation}
%
where $\dot\gamma$ is the dimensionless shear rate and ${\bf e}_x$ and ${\bf e}_y$
are horizontal and vertical unit vectors, respectively.  
The initial bilayer structure consists of a small self-enclosing bilayer (vesicle) and several pieces of bilayers.
Figure~\ref{fig:BC1_shear}(a)--(c)
shows snapshots of the bilayer when $\dot\gamma= 0.05,0.075,0.01$
at $t = 0.5$ $\upmu$s.
The dynamics of the bilayer can be found in the supplementary movies, which show that the initial pieces of bilayers merge and form a worm-like shape
under a linear shear flow.
At a low shear rate, the bilayer constantly goes through rotation and extensional deformation with the whole bilayer intact (figure~\ref{fig:BC1_shear}(a)).
As the shear rate increases to a moderate value (figure~\ref{fig:BC1_shear}(b)), the bilayer is observed to shed a small piece of bilayer, 
similar to the asymmetric breakup of a viscous drop \cite{}.
In figure~\ref{fig:BC1_shear}(c) the high shear rate gives rise to two separate, nearly equal bilayers, 
similar to the symmetric drop breakup under a linear shear flow \cite{}.
%%
%\begin{figure}
%  \begin{center}
%    \includegraphics[width=1.0\textwidth]{Figures/Figure5.pdf}    
%  \end{center}
%  \vspace{-20pt}  
%  \caption{\label{fig:BC1_TG} Multiple component bilayers in a Taylor-Green when $V_0 = \{0.1, 0.15, 0.2\}$ at $t=0.2\ \mu$s. The pre-relaxed initial configuration is shown in inset of panel (a). 
% The streamlines are plotted in the background. 
%Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
%  }
%\end{figure}

In terms of deformation measures,  
the free energies 
are relatively constant (Figure~\ref{fig:BC1_shear}(d)),
with the overall changes in the range of a few kT/nm.  
Note that the free energy $F$ in figure~\ref{fig:BC1_shear}(d) has the unit of force because our system is two dimensional.

An interesting feature of the simulations is that the order parameter $\tilde S_2$ in figure~\ref{fig:BC1_shear}(e)
is on average increasing.  In the initial configuration,
the structure has three or four components.  
%
Under the shear flow, the shedding and merging of bilayers
result in an overall decrease in distinct bilayer structures.  
This suggests that
the shear flow changes the energy landscape to move the local equilibrium obtained from a random initial condition
to an alternate local equilibrium with greater orientational order.   
%
%\begin{figure}
%  \begin{center}
%    \includegraphics[width=1.0\textwidth]{Figures/Figure6.pdf}        
%  \end{center}
%\caption{\label{fig:ves_TG} Single vesicle in a TG flow. Panels (a)-(c) are snapshots for $V_0=\{0.1, 0.15, 0.2\}$ at $t=0.6\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a). The streamlines are plotted in the background.
%Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
%}
%\end{figure}
%
Finally, the strain parameter diverges in the large shear flow rate cases (Figure~\ref{fig:BC1_shear}(f))
because the components eventually completely separate and move away from one another
under the shear flow.

%%%
\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure4.pdf}
  \end{center}
  \caption{
    \label{fig:Ves_shear}
The figure shows a single vesicle in a shear flow. Panels (a)-(c) are snapshots for $\dot \gamma = \{0.05, 0.0655, 0.075\}$ at $t=0.16\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a).
The streamlines are plotted in the background.
Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
     }
\end{figure}
%
In \citet{Fu2022_JFM} the hydrodynamics of a JP vesicle under a linear shear flow is studied. 
Focusing on drawing analogies to hydrodynamics of a vesicle in continuum modeling (such as tank-treading, bilayer slip and permeability),
our previous studies also show the existence of a critical shear rate above which the JP vesicle ruptures. 
Based on the these early results, we conduct numerical simulations with $\dot\gamma=0.05, 0.066, 0.075$.
At these shear rates, the vesicle undergoes the familiar hydrodynamics (such as elongation along the extensional axis and tank-treading motion),
as shown in Figure~\ref{fig:Ves_shear} (a)--(c).
%
Here we illustrate how the three measures of structural deformation 
correlate to the dynamics of a JP vesicle.
We reinitialized the case (i) configuration with particles arranged in the pattern of a single, circular vesicle.
This shape is also a local equilibrium, with somewhat less energy than the disordered state c.f.,
Figure~\ref{fig:BC1_shear}(d) and Figure~\ref{fig:Ves_shear} (d).

Unlike the dynamics of bilayers in figure~\ref{fig:BC1_shear}, 
the energies of the JP vesicle in figure~\ref{fig:Ves_shear}(d) show jumps from the baseline value $30$ kT/nm to 32 kT/nm
signaling the rupture of the vesicle into disconnected bilayers
(see figure \ref{fig:Ves_shear}(d), long and short dashed curves).
After the rupture, each piece circles around the vorticity at the center without reconnection while the energies fluctuate slightly around a constant.

For the lowest shear rate case, the vesicle has nearly constant orientational order $\tilde S_2 = 1$
(see figure \ref{fig:Ves_shear}(e), solid curve).
After the JP vesicle
ruptures with $\dot\gamma= 0.066$ and $\dot \gamma= 0.075$,
we observe a greater variation in the order parameter $\tilde{S}_2$
with a baseline value around $0.7$
(see figure \ref{fig:Ves_shear}(e), dashed curves).
The oscillations occur due to the orbit of the two bilayer components,
and $\tilde{S}_2$ increases to about $0.9$ when the components slide past one another and are nearly parallel.
%
As in the previous case, peaks in the strain parameter $E$ correlate well with changes in structural topology in the bilayer dynamics, see
the dashed curves in figure~\ref{fig:Ves_shear}(f).

%%%%%%%
%
\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure5.pdf}    
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC1_TG} Multiple component bilayers in a Taylor-Green when $V_0 = \{0.1, 0.15, 0.2\}$ at $t=0.2\ \mu$s. The pre-relaxed initial configuration is shown in inset of panel (a). 
 The streamlines are plotted in the background. 
Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
  }
\end{figure}
%
\subsection{Bilayer and vesicle configurations in a Taylor-Green flow}
Next, we subject the bilayer/vesicles configurations to a 
Taylor-Green (TG) background flow
\begin{equation}
\label{eq:tg_flow}
\uu_\infty(\xx) = V_0\; \frac{\text{nm}}{\text{ns}}\;
\left(
-\cos\left(\frac{{\bf e}_x\cdot\xx}{\lambda}\right)
 \sin\left(\frac{{\bf e}_y\cdot\xx}{\lambda}\right)
         {\bf e}_x
         +\sin\left(\frac{{\bf e}_x\cdot\xx}{\lambda}\right)
         \cos\left(\frac{{\bf e}_y\cdot\xx}{\lambda}\right)
             {\bf e}_y\right).
\end{equation}
The TG flow is a confining flow consisting of a checkboard pattern
of cells with alternating circulation.  We control the flow by the
the dimensionless flow strength $V_0$ and with the cell size $\lambda = l$ nm.
The default parameter $l=2$ is used through this work.
%

\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure6.pdf}        
  \end{center}
\caption{\label{fig:ves_TG} Single vesicle in a TG flow. Panels (a)-(c) are snapshots for $V_0=\{0.1, 0.15, 0.2\}$ at $t=0.6\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a). The streamlines are plotted in the background.
Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
}
\end{figure}
